Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-06 report.Rmd
clean for docker

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r, include=FALSE}
tar_load(lalt_pool_grid_png)
```

@@

```{r, include=FALSE}
tar_load(lalt_sep_grid_png)
```

@@

```{r, include=FALSE}
tar_load(lalt_tree_grid_png)
```

@@

```{r, include=FALSE}
tar_load(ratio_png)
```

@@

```{r, include=FALSE}
tar_load(lma_ld_png)
```

@@

```{r, include=FALSE}
tar_load(cv_pool_png)
```

@@

```{r, include=FALSE}
tar_load(cv_sep_png)
```

@@

```{r, include=FALSE}
tar_load(petiole_png)
```
